---
title: "CarreFour Feature Selection IP"
output: html_document


##  CarreFour Kenya Sales increment strategies .
### 1. Research Question
DA data analyst at Carrefour Kenya and are currently undertaking a project that will inform the marketing department on the most relevant marketing strategies that will result in the highest no. of sales (total price including tax).


### 2. Metric of Success

Identify the association rules of product transactions in the store.

### 3. Understanding the context.
The provided data has been acquired from the carre four stores in Kenya of transactions that have been made over time and my goal of 
this research is to come up with insights from the analysis.

### 4. Recording the Experimental Design

a. Data Loading
b. Data Cleaning and preprocessing
c. Exploratory Data Analysis
d. Associative rules implememntation
e. Recommendations and Conclusions.

### 5. Data Relevance.

The provided data is relevant for this kind of study since it has a reflection of how current transactions happen and the association it portrays.

### Data Preview

#### Loading the libraries
```{r}
library(modelr)
library(broom)
library(caret)
library(rpart)
library(ggplot2)
library(Amelia)
library(dplyr)
library(data.table)
library(tidyverse)
```

#### Loading the data

```{r}
sales <- fread('http://bit.ly/SupermarketDatasetII')
head(sales)
```

checking out the dataset
```{r}
str(sales)
```

Converting entries to transactions.
```{r}
library(arules)

path <-"http://bit.ly/SupermarketDatasetII"

Transactions<-read.transactions(path, sep = ",")
Transactions
```


Verifying the object's class
```{r}
class(Transactions)
```

previewing our first 5 transations.
```{r}
inspect(Transactions[1:5])
```

Previewing items that make up our dataset
```{r}
items<-as.data.frame(itemLabels(Transactions))
colnames(items) <- "Item"
head(items, 10) 
```

summary of the transaction dataset.
```{r}
summary(Transactions)
```

Exploring frequency of some articles at index 3 to 8.
```{r}
itemFrequency(Transactions[, 3:8],type = "absolute")
round(itemFrequency(Transactions[, 3:8],type = "relative")*100,2)

```

Build the model
model 1 : support =0.001 and confidence = 0.8
```{r}
sales.rules <- apriori (Transactions, parameter = list(supp = 0.001, conf = 0.8))
sales.rules

```

model 1 has 74 rules.


model 2 : support =0.002 and confidence = 0.8
```{r}
sales.rules2 <- apriori (Transactions, parameter = list(supp = 0.002, conf = 0.8))
sales.rules2

```

model 2 has 2 rules which means alot of ossible rules will be overlooked. 


model 3 : support =0.002 and confidence = 0.6
```{r}
sales.rules3 <- apriori (Transactions, parameter = list(supp = 0.002, conf = 0.6))
sales.rules3

```
model 3 produces 43 rules.


Exploring our model
```{r}
summary(sales.rules)

```


Observing rules built in our model
```{r}
inspect(sales.rules[1:5])
```


```{r}
summary(sales.rules)
```

### Recommendations.
The best set of rules is model 3 with a support of 0.002 and confidence of 0.6.


### Follow up questions.
#### Did we have enough data for the study?
yes

#### Was the data relevant?
yes

