---
title: "CarreFour Feature Selection IP"
output: html_document


##  CarreFour Kenya Sale Increment Strategies.
### 1. Research Question

Carrefour Kenya and are currently undertaking a project that will inform the marketing department on the most relevant marketing strategies that will result in the highest no. of sales (total price including tax).This project is aimed at doing analysis on the dataset provided by carrefour and create insights on how to achieve highest sales. 


### 2. Metric of Success

Achieving a set of variables that are important and influences the sales variable.

### 3. Understanding the context.

CarreFour is an International chain of retail supemarkets in the world, It was set up in Kenya in the year 2016 and has been performing well over the years.
This project is aimed at creating insights from existing and current trends to develop marketing strategies that will enable the marketing team achieve higher sales.

### 4. Recording the Experimental Design

a. Data Loading
b. Data Cleaning and preprocessing
c. Exploratory Data Analysis
d. Implementation o solution.
e. Recommendations and Conclusions.

### 5. Data Relevance.

The provided data is relevant for this study since it's been sourced from CarreFour database and is a reflection of current transactions.


### Data Preview

#### Loading the libraries
```{r}
library(modelr)
library(broom)
library(caret)
library(rpart)
library(ggplot2)
library(Amelia)
library(dplyr)
library(data.table)
library(tidyverse)
```

#### Loading the data
```{r}
carrefour <- fread('http://bit.ly/CarreFourDataset')
carrefour
```

#### Checking on the first 6 entries
```{r}
head(carrefour, 6)
```

#### checking on last 6 entries
```{r}
tail(carrefour, 6)
```

#### checking on data types
```{r}
str(carrefour)
```

#### Checking on dataset description
```{r}
summary(carrefour)
```

#### checking the size/shape of a dataframe 
```{r}
dim(carrefour)
```

### Data Preprocessing.

#### i. Completeness
This is achieved by checking for missing values if any imputed to ensure correct predictions are made.
```{r}
is.null(carrefour)
```

##### Total number of null valuesin dataset
```{r}
total_null <- sum(is.na(carrefour))
total_null
```

#### ii. Consistency.
Consistency is achieved when all the duplicated rows are done away with.
```{r}
duplicated_rows <- carrefour[duplicated(carrefour), ]
duplicated_rows
```

```{r}
anyDuplicated(carrefour)
```

#### iii. Relevance.

Relevance is achieved by ensuring all the features provided for the analysis are relevant to the objective Which in this case all provided features are.

#### iv. Accuracy.

Checking that all entries are correct.

#### Outliers
We can visualize any outliers in a dataset using boxplots

```{r}

colnames(carrefour)

```

###### Renaming column names
```{r}

# Rename column where names 
names(carrefour)[names(carrefour) == "Invoice ID"] <- "Invoice_ID"
names(carrefour)[names(carrefour) == "Customer type"] <- "Customer_type"
names(carrefour)[names(carrefour) == "Product line"] <- "Product_line"
names(carrefour)[names(carrefour) == "gross margin percentage"] <- "gross_margin_percentage"
names(carrefour)[names(carrefour) == "Unit price"] <- "Unit_price"
names(carrefour)[names(carrefour) == "gross income"] <- "gross_income"
colnames(carrefour)
```

```{r}
str(carrefour)
```

a. Unit Price.
```{r}
a <- carrefour$Unit_price
boxplot(a)

```

b.Quantity
```{r}
quantity <- carrefour$Quantity
boxplot(quantity)

```

c. cogs
```{r}
cogs <- carrefour$cogs
boxplot(cogs)

```

d. Gross margin percentage
```{r}
b <- carrefour$gross_margin_percentage
boxplot(b)

```

e. Gross income
```{r}
gross_income <- carrefour$gross_income
boxplot(gross_income)

```

e. Rating 
```{r}
rating <- carrefour$Rating 
boxplot(rating)

```

e. Total 
```{r}
total <- carrefour$Total 
boxplot(total)

```

###### The total and gross income have outliers .

 To see the number of outliers
 
Gross Income
```{r}
a <- carrefour$gross_income
boxplot.stats(a)$out

```
The outlier entries are 9. 

Total
```{r}
a <- carrefour$Total
boxplot.stats(a)$out

```
The outlier entries are 9. 


### Exploratory Data Analysis.
#### Univariate Analysis.

a. Unit Price
```{r}
mean(carrefour$Unit_price, trim = 0, na.rm=FALSE)
median(carrefour$Unit_price,na.rm=FALSE)
range(carrefour$Unit_price,na.rm=FALSE, finite=FALSE)
quantile(carrefour$Unit_price, probs=seq(0, 1,0.25), na.rm=FALSE, names=TRUE, type=7)
var(carrefour$Unit_price)
sd(carrefour$Unit_price,na.rm=FALSE)
```

mode
```{r}
getmode <- function(v){
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
```

```{r}
unit_price_mode <- getmode(carrefour$Unit_price)
unit_price_mode

```

 Visualizing Unit Price.
```{r}
d<-hist(carrefour$Unit_price, breaks=10, col="red", xlab="Unit price",main="Unit price")
plot(d)
```
The highest unit prices are between 20-30, 70-80 and 90-100.


```{r}
head(carrefour)
```


b. Quantity
```{r}
hist(carrefour$Quantity, breaks=12, col="skyblue",xlab="Quantity", main='Quantity of Products')
```
Most product quantities bought are 1 or 2.

c. Tax.
```{r}
d <- density(carrefour$Tax, xlab="Tax")
plot(d)
```


d. cogs
```{r}
cogs <- hist(carrefour$cogs, xlab="cogs")
plot(cogs)
```
The highest number of cogs is at zero but the occurence reduces as the value of cogs increases.

e. gross margin percentage 
```{r}
#plot(gross_margin)
```
The gross margin percentage  range between 2 to 8.


```{r}
head(carrefour)
```


### Bivariate Analysis.
Covariance 
Covariance is the statistical representation of the degree to which two variables vary from each other.

#### Covariance.
```{R}
carrefour_cov <- carrefour[,c(6,7,8,12,14,16)]
cov(carrefour_cov)
```

#### Correlation.
```{R}
carrefour.cor <- cor(carrefour_cov, method=c('spearman'))
```

visualizing
```{R}
#install.packages('corrplot')
library(corrplot)
corrplot(carrefour.cor)
```
cogs,gross income, tax and total are highly correlated to each other.


### IMPLEMENTATION.
1. Feature Selection.
```{r}
carrefour_1 <- carrefour
head(carrefour_1)
```

### 1. Filter Method.
Applies a metric to assign a score to each feature, then features are then ranked by the score.
It uses a correlation function therefore removes redundancy using correlation.

```{r}
carrefour_2 <- carrefour_1[,c(6,7,8,12,14,15,16)] 
head(carrefour_2)

```

Libraries
```{r}
library(caret)
library(corrplot)

```


Calculating the correlation matrix
```{r}
correlationMatrix <- cor(carrefour_2)

# Find attributes that are highly correlated
highlyCorrelated <- findCorrelation(correlationMatrix, cutoff=0.75)
head(highlyCorrelated)
head(carrefour_2)

```

Variables that are highly correlated are at index 4,7 and 3 they include; tax, cogs and total.


We will remove these variables then compare the results graphically.
```{R}
# Removing Redundant Features 
carrefour_22 <-carrefour_2[,-c(3,4,7)]
head(carrefour_22)

correlationmatrix <- cor(carrefour_22)

# Performing our graphical comparison
par(mfrow = c(1, 2))
corrplot(correlationMatrix, order = "hclust")
corrplot(correlationmatrix, order = "hclust")

```


### Conclusion.
Important features for this research are unit price, quantity, gross income and rating.

### Follow up questions.
#### Did we have enough data for the study?
yes

#### Was the data relevant?
yes

